### 2021-09-10 analysis/fit_models.Rmd
Added a reparameterised model which returns good likelihoods but can't reverse engineer for a fit....code/package quite messy but going to just keep backed up and fix later once we have this working. ATM it is changing to often to make spending loads of time cleaning it up worth while. Its a mess, but its logical to follow and can be cleaned up once its sorted and we no longer need to mess with the guts

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "URWHelvetica", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")
```

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "URWHelvetica", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")

```

## Trial run of a single site using new routine

Using the new routine in this branch (using Nelder-Mead simplex rather than COBYLA) and seperatly optimising p.

```{r}
# Run model analysis lots and lots of times.

bel <- get_data() %>%
  filter(site == "BEL")

result_data <- purrr::map_df(
  seq_len(10),
  ~ {
    print(paste("Itteration", .x))
    result <- run_analysis(bel, n = 10, upper = 0.1, verbose_r = T, verbose = F)
    return(
      data.frame(
        ll = result$fmax,
        p = result$est[1],
        ls = result$est[2],
        ln = result$est[3],
        qn = result$est[4],
        a = result$est[5]
      )
    )
  }
)

best_mod <- result_data %>% filter(ll == max(ll))
params <- best_mod %>% select(p, ls, ln, qn, a)
solution <- list(
  fmax = best_mod$ll,
  data_name = "all",
  est = params %>% as.double()
)
solution

result_data %>%
  gather("measurement", "value", -ll) %>%
  ggplot(aes(x = value, y = ll)) +
  geom_point() +
  facet_wrap(~measurement, scale = "free")

```

```{r}
# convert new parameters to the old ones and show the fit
# ls = bs*as
# ln = br*ar^2
# qn = ar / as
# alpha = ar - as
formated_solution <- solution
formated_solution$est[2] <- solution$est[2] * solution$est[4]
formated_solution$est[3] <- solution$est[3] * solution$est[5]^2
formated_solution$est[4] <- solution$est[5] / solution$est[4]
formated_solution$est[5] <- solution$est[4] - solution$est[5]

# check likelihood
loglike_model_all(
  bel$foraging_distance,
  formated_solution$est[1], formated_solution$est[2],
  formated_solution$est[3], formated_solution$est[4],
  formated_solution$est[5]
)

# show fit of the best model to the data
make_full_plot(
  bel$foraging_distance,
  list("collective" = formated_solution),
  subplot_coords = c(0.5, 8, -4.5, -2.5)
)

```

```{r}
# examine likelihood space of best model
map_likelihood_space(bel$foraging_distance, params, n = 10000, upper = 0.1)

# sanity check
loglike_model_all_new(
  bel$foraging_distance,
  params[[1]], params[[2]],
  params[[3]], params[[4]],
  params[[5]]
)

loglike_model_all(
  bel$foraging_distance,
  params[[1]], params[[2]],
  params[[3]], 5,
  params[[5]]
)

```
